Analysis-ready VCF at Biobank scale using Zarr

### 2025-01-23 paper.tex
First v. rough draft of GPU stuff

>>>>

\subsection{Extensibility: GPU acceleration}
[JK: this is a super rough first narrative draft.]
Machine learning, and in particular deep learning methods, have led to 
major breakthroughs in many different fields in recent years [CITES].
GPUs have been a key enabling factor in this [details and cites].
The PyData ecosystem [cites] has also enabled this. Techologies like
[Cupy, lots of others] substantially lower the bar for writing efficient
GPU code.
Deep learning methods depend crucially on efficient access to vast 
datasets for training, and Zarr is emerging as a popular choice
[cites from geosciences?]. The RAPIDs GPU Accelerated data science 
library [which does] now supports Zarr through [kvikio, more?].

To demonstrate the ease and efficiency with this data stored in Zarr 
format can be processed on a GPU, we developed two proof-of-concept
applications. In the first we re-implement the af-dist calculation
used throughout as an example of a non-trivial whole-matrix operation
on GPU. In the second, we demonstrate some emerging technology 
in which Zarr data can be decompressed directly in GPU memory. 
In both cases we demonstrate on chromosome 22 of 
1000 Genomes WGS data~\citep{byrska2022high}.

[Details of af-dist benchmark]

[Details of decompression benchmark]
